---
title: "Co-Occurance"
author: "Jason Heppler"
date: "10/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Tag co-occurance

```{r}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(tidytext))
suppressPackageStartupMessages(library(widyr))

suppressPackageStartupMessages(library(tidygraph))
suppressPackageStartupMessages(library(ggraph))
suppressPackageStartupMessages(library(network))
suppressPackageStartupMessages(library(igraph))
```

## Word Co-Occurance

```{r}
data_keyword <- tibble(id = data$key, 
                       keyword = data$tags) %>%
  unnest(keyword)
```

Check that we're getting consistent counts. 

```{r}
data_keyword %>%
  count(keyword, sort = TRUE)
```

To remove duplicates due to capitalization, we lowercase everything. 

```{r}
data_keyword <- data_keyword %>% 
  mutate(keyword = tolower(keyword))
```

### Word Co-occurences and correlations

```{r}
word_pairs <- data_keyword %>% 
  pairwise_count(keyword, id, sort = TRUE, upper = FALSE)
word_pairs
```

Plotting these keyword pairs. 

```{r}
library(ggplot2)
library(igraph)
library(ggraph)

set.seed(1234)
network_word_pairs <- word_pairs %>%
  filter(n >= 20) %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = n, edge_width = n), edge_colour = "steelblue") +
  geom_node_point(size = 5) +
  geom_node_text(aes(label = name), repel = TRUE, 
                 point.padding = unit(0.2, "lines")) +
  theme_void()

network_word_pairs

ggsave(filename = "results/network_wordpairs.png", plot = network_word_pairs, width = 18, height = 16, units = "cm")
```

## Network of Keywords

```{r}
keyword_pairs <- data_keyword %>% 
  pairwise_count(keyword, id, sort = TRUE, upper = FALSE)

keyword_pairs

set.seed(1234)
network_keyword_pairs <- keyword_pairs %>%
  filter(n >= 2) %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = n, edge_width = n), edge_colour = "royalblue") +
  geom_node_point(size = 1) +
  geom_node_text(aes(label = name), repel = TRUE,
                 point.padding = unit(0.2, "lines")) +
  theme_void()
network_keyword_pairs

#ggsave(filename = "results/network_keywordpairs.png", plot = network_keyword_pairs, width = 22, height = 16, units = "cm")
```
We can also look at the correlation of keywords. 

```{r}
keyword_cors <- data_keyword %>% 
  group_by(keyword) %>%
  filter(n() >= 50) %>%
  pairwise_cor(keyword, id, sort = TRUE, upper = FALSE)

keyword_cors
```

Let's visualize keyword correlations. 

```{r}
set.seed(1234)
network_keywordcors <- keyword_cors %>%
  filter(correlation >= .0) %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = correlation, edge_width = correlation), edge_colour = "cyan4") +
  geom_node_point(size = 5) +
  geom_node_text(aes(label = name), repel = TRUE,
                 point.padding = unit(0.2, "lines")) +
  theme_void()

network_keywordcors

ggsave(filename = "results/network_keywordcors.png", plot = network_keywordcors, width = 18, height = 16, units = "cm")
```


Let's also look at keywords that *don't* correlate often together. 

```{r}
set.seed(1234)
network_keyword_neg_cors <- keyword_cors %>%
  filter(correlation <= -.0) %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = correlation, edge_width = correlation), edge_colour = "cyan4") +
  geom_node_point(size = 5) +
  geom_node_text(aes(label = name), repel = TRUE,
                 point.padding = unit(0.2, "lines")) +
  theme_void()
network_keyword_neg_cors

ggsave(filename = "results/network_keyword_neg_cors.png", plot = network_keyword_neg_cors, width = 18, height = 16, units = "cm")
```

